The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-06 document/ms.tex
Adding occurrence rate table into ms
gamma

Assuming a Poisson likelihood, the occurrence rate density in a volume
$V$~--~defined as $P_\mathrm{min} \le P < P_\mathrm{max}$ and
$R_\mathrm{min} \le R < R_\mathrm{max}$~--~is
\begin{eqnarray}
\frac{\dd N}{\dd\ln P\dd\ln R} &=&
    \frac{N(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
         {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
\end{eqnarray}
where $N(\cdots)$ is the number of planets in the volume and
\begin{eqnarray}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &=&
    \sum_{k=1}^{K} \int p(w_{P,\,R})\,Q_k(w)\,\bvec{1}[P,\,R\in V]\dd w
\end{eqnarray}
where $p(w_{P,\,R})$ is the prior distribution of all the parameters except
the period and radius.
Using the $J$ injections sampled uniformly in period and radius and other
parameters from $p(w_{P,\,R})$,
\begin{eqnarray}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &\approx&
    \frac{K}{J}\,\sum_{j=1}^{J} Q_k(w^{(j)})
\end{eqnarray}
where the sum is over all injections in the volume $V$.

>>>>

Assuming a Poisson likelihood, the occurrence rate density in a volume
$V$~--~defined as $P_\mathrm{min} \le P < P_\mathrm{max}$ and
$R_\mathrm{min} \le R < R_\mathrm{max}$~--~is
\begin{eqnarray}\eqlabel{rate-density}
\Gamma_V \equiv \frac{\dd N}{\dd\ln P\dd\ln R} &=&
    \frac{C(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
         {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
\end{eqnarray}
where $N$ is the expected number of planets per G/K dwarf, $C(\cdots)$ is the
number of planets in the volume, and
\begin{eqnarray}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &=&
    \sum_{k=1}^{K} \int p(w_{P,\,R})\,Q_k(w)\,\bvec{1}[P,\,R\in V]\dd w
\end{eqnarray}
where $p(w_{P,\,R})$ is the prior distribution of all the parameters except
the period and radius.
Using the $J$ injections sampled uniformly in period and radius and other
parameters from $p(w_{P,\,R})$,
\begin{eqnarray}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &\approx&
    \frac{K}{J}\,\sum_{j=1}^{J} Q_k(w^{(j)})
\end{eqnarray}
where the sum is over all injections in the volume $V$.

\begin{floattable}
\begin{deluxetable}{ccc}
\tabletypesize{\footnotesize}
\caption{The occurrence rate density in two radius bins \label{tab:occurrence}}
\include{ortab}
\tablenotetext{a}{See \eq{rate-density}}
\tablecomments{These values are computed in the period range 2--25~years.}
\end{deluxetable}
\end{floattable}
